\documentclass[9pt]{developercv}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.38\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\colorbox{maincolor}{{\huge\textcolor{white}{\textbf{\MakeUppercase{Stanisław}}}}} % First name
	
	\colorbox{maincolor}{{\huge\textcolor{white}{\textbf{\MakeUppercase{Swianiewicz}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{11}{Złota 44, 05-123 Chotomów}\\
	\icon{Phone}{11}{+48 661 471 272}\\
	\icon{At}{11}{\href{mailto: se@stswn.pl }{se@stswn.pl}}\\	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{11}{\href{https://stswn.pl}{stswn.pl}}\\
	\icon{Linkedin}{11}{\href{https://www.linkedin.com/in/sswianiewicz}{linkedin.com/in/sswianiewicz}}\\
	\icon{Github}{11}{\href{https://github.com/stswn}{github.com/stswn}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{About me}

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I am a software engineer with over 13 years of professional experience. I specialize in JVM based technologies and have practical knowledge of front end web development. I am a strong proponent of functional programming and static typing. Scala is my language of choice. I care about good programming practices, clean and testable code, and engineer-friendly software architecture.

    I prefer to work in hybrid mode with few days spent in the office or fully remotely.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Functional Programming}{75}
		\baritem{Scala}{95}
		\baritem{Java}{55}
		\baritem{Typescript, Javascript}{35}
		\baritem{React}{35}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{1/CI\simslash CD, 3/git, 3/SQL, 2/Docker, 2/k8s}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{since 11/2023}
		{Senior Software Engineer}
		{Synerise}
    {Synerise is a Polish startup providing a behavioral data platform that helps companies understand customers' actions and better respond to their needs in real time. At Synerise I am part of a back end team working on automation services that allow Synerise users to create workflows which handle large number of customer events in real time.\\
		\texttt{Scala}\slashsep\texttt{PostgreSQL}\slashsep\texttt{Scylla}\slashsep\texttt{k8s}}

	\entry
		{11/2021 -- 10/2023}
		{Senior Software Engineer}
		{Schibsted, Rocker}
    {Rocker is a Swedish fintech startup aiming to provide a comprehensive solution for managing everyday finances. During my time at Rocker I was working on various back end services, mainly in Loan \& Credit area.\\
		\texttt{Scala}\slashsep\texttt{ZIO}\slashsep\texttt{PostgreSQL}\slashsep\texttt{k8s}\slashsep\texttt{GCP}}

	\entry
		{10/2019 -- 10/2021}
		{Senior Software Engineer}
		{ING Tech PL}
		{At ING I worked on end user facing application which is a part of a large KYC (Know Your Customer) solution developed by Wholesale Banking Advanced Analytics (WBAA) team. I was mainly focusing on design, maintenance and development of a REST API serving transactions data but was also involved in UI development.\\
		\texttt{Scala}\slashsep\texttt{ZIO}\slashsep\texttt{Oracle}\slashsep\texttt{React}\slashsep\texttt{k8s}}

	\entry
		{11/2017 -- 9/2019}
		{Software Developer}
		{JT Weston}
		{JT Weston is a company behind Makigami (Neula) business process automation platform. I was involved in development of both: back-end and front-end components of advanced workflow application based on CQRS / Event Sourcing architecture.\\
		\texttt{Scala}\slashsep\texttt{Akka}\slashsep\texttt{PostgreSQL}\slashsep\texttt{AngularJS}}
	\entry
		{2013 -- 2017}
		{Software Developer}
		{SER Solutions}
		{Doxis4 by SER is the largest ECM (Enterprise Content Management) solution created in Europe. I worked on various components of this system:
		\begin{itemize}
			\item mobileCube - mobile client for the ECM system (Android application and Java middleware) \\ \texttt{Java}\slashsep\texttt{Android}\slashsep\texttt{Spring}
			\item CMIS protocol connector for the ECM system \\ \texttt{Scala}\slashsep\texttt{Apache Tomcat}
		\end{itemize}}
	\entry
		{2012 -- 2013}
		{Software Engineer}
		{SAFIRA (now part of KPMG)}
		{During my time at this conultancy company I worked on a project based on IBM BPM workflow solution for a big insurance company. \\ \texttt{IBM BPM}\slashsep\texttt{Alfresco}}
	\entry
		{2011 -- 2012}
		{ECM/BPM Consultant}
		{Xentivo}
		{I worked on two document management projects for RWE (now Innogy) and Warsaw City Hall. \\ \texttt{Liferay}\slashsep\texttt{Documentum}}
	\entry
		{2010 \\\footnotesize{part time}}
		{Java programmer}
		{Torn}
		{I worked on jPalio Designer -- Eclipse IDE plugin used by company developers for developing applications in company's proprietary framework jPalio.}
			
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2006 -- 2012}
		{Master's Engineering Degree in Computer Science}
		{Warsaw University of Technology}
		{Thesis subject: "Neural and evolutionary techniques of identification and tuning of Fuzzy Systems" \\ \textit{I completed my studies with a grade of very good}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Polish} - native \\ \textbf{English} - proficient
\end{minipage}
\hfill
\begin{minipage}[t]{0.7\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love being outside: trekking, climbing, skiing. I live close to a forest and love to walk my dog or go for a run. When nobody is listening, I like to play guitar or tin whistle.
\end{minipage}
\end{document}
